\begin{battlespecial}{Endgame - Repatriation}
\battleinfo{Defeat Ashnard}{2}{\ike, \marcia, \tanith, \reyson, \elincia, \mordecai}
\base{
    \item Manage:
    \begin{itemize}
        \item Skills:
        \begin{itemize}
            \item \ike:
            \begin{itemize}
                \item Assign Wrath and Resolve
            \end{itemize}
        \end{itemize}
    \end{itemize}
}
\prep{
    \units{
        \item Remove Mist
    }
    \map{
        \swap{Ena}{\elincia}
        \swap{Ena}{\tanith}
        \swap{\reyson}{\mordecai}
    }
}
\begin{enumerate}
\turn{
    \ikef
    \movewait{4U, 1R}
    \Xmove{2}{\elincia}
    \movewait{7U}
    \Xmove{1}{\marcia}
    \moveunequip{6U}
    \item (X 2R) \mordecai:
    \begin{itemize}
        \move{1U, 1R}
        \item Smite \reyson
    \end{itemize}
    \reysonf
    \movewait{2L, 3U}
    \Xmove{1}{\tanith}
    \moveunequip{9U}
    \item On Enemy Phase:
    \begin{itemize}
        \item \tanith\ will probably die, but is intended and faster. Her role is to lure the \enemy{Generals} out of the way.
    \end{itemize}
    \turnend
}
\turn{
    \item Choose whatever laguz royal, it doesn't matter
    \ikef
    \moveuse{1R}{Pure Water}
    \marciaf
    \begin{itemize}
        \item Rescue \ike
    \end{itemize}
    \canto{1L, 10U}
    \item (2X 1U) \elincia:
    \begin{itemize}
        \move{2R, 2U}
        \use{Rescue on \reyson}
    \end{itemize}
    \canto{3D}
    \reysonf
    \begin{itemize}
        \move{5U}
        \item Chant Marcia
    \end{itemize}
    \marciaf
    \begin{itemize}
        \move{11U}
        \item Drop \ike\ left
    \end{itemize}
    \turnend
}
\end{enumerate}
\end{battlespecial}

\begin{tcolorbox}[title=\begin{center}Endgame - Repatriation\end{center},colbacktitle=blue!50!white]
\begin{itemize}
    \item A bishop should attempt to put \marcia\ to sleep. The result of this doesn’t matter.
    Then \enemy{Ashnard} should move towards \ike\ and attack.
    \vspace{2mm}
    \item Ideal outcome: \enemy{Ashnard} hits \ike\ (displayed ~65-85\%) and activates Resolve + Wrath and gets a crit (two chances of 50\% crit rates)

    \item Other outcomes:
    \begin{itemize}
        \item \enemy{Ashnard} hits \ike\, but \ike\ doesn’t crit: just finish off \enemy{Ashnard} during next player phase. \ike\ has a 100\% hitrate with resolve, so he’s guaranteed to kill \enemy{Ashnard}
        \item \enemy{Ashnard} misses \ike\ (he has a 63-83\% displayed hitrate): the game hates you. Run away with \marcia\ (all right all down), run away with \elincia\, have \ike\ stay in place, and really hope he gets hit next enemy phase.
        \item If \#2 happens and \enemy{Ashnard} misses \ike\ AGAIN: the game hates you. Game Over.
    \end{itemize}
\end{itemize}
\end{tcolorbox}
